Pleiotropy of expression quantitative trait loci increases with the number of regulated genes, active cell types and tissues and bound transcription factors

### 2023-01-10 ms/ms06_floats.tex
MS

% full size table is table
\begin{table}[!tbp]
\centering
\scriptsize
%\hline
\csvreader[separator=tab,
tabular=crclcp{0.4\textwidth},
head,
table head=\bfseries Chrom. & \bfseries Pos (hg38) & \bfseries Cytoband & \bfseries RSID & \bfseries Marker & \bfseries GWAS Categories\\\hline,
]{\floatRelativePath/cmpt_count_per_rsid.py/count_per_rsid_gwas_ms.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv\ & \csvcolv\ & \csvcolvi}% specify your coloumns here
%\hline
%
\vspace{15pt}
%
\caption{eQTLs involved in four GWAS categories. The gene marker is the eQTL gene with highest PubMed publication count.}
\label{tab:pleitropic_variants}
\end{table}

>>>>

% full size table is table
\begin{table}[!tbp]
\centering
\scriptsize
%\hline
\csvreader[separator=tab,
tabular=crclcp{0.4\textwidth},
head,
table head=\bfseries Chrom. & \bfseries Pos (hg38) & \bfseries Cytoband & \bfseries RSID & \bfseries Marker & \bfseries GWAS Categories\\\hline,
]{\floatRelativePath/cmpt_count_per_rsid.py/count_per_rsid_gwas_ms.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv\ & \csvcolv\ & \csvcolvi}% specify your coloumns here
%\hline
%
\vspace{15pt}
%
\caption{Example eQTLs involved in four GWAS categories in different cytobands.
The whole list is given in the Supplementary files.
The gene marker is the eQTL gene with the highest PubMed publication count.}
\label{tab:pleitropic_variants}
\end{table}
